---
title: "Analysis of Melanoma dataset using CellChat"
author: "Marta Interlandi"
date: "9/15/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

```{r setup_environment, message=FALSE, warning=FALSE}
library(Seurat) 
library(CellChat)
```

## Preparing data

We load the melanoma Seurat object that was previously generated (see /input_data/melanoma/) and create a CellChat object. All steps of this analysis are following CellChat [tutorial](https://htmlpreview.github.io/?https://github.com/sqjin/CellChat/blob/master/tutorial/CellChat-vignette.html).

```{r cnvuo}
melanoma <- readRDS(file = "/marta_home/InterCellar-reproduc/InterCellar-reproducibility/input_data/melanoma/melanoma_seuobj.rds")

melanoma <- NormalizeData(melanoma)
melanoma <- createCellChat(melanoma, group.by = "cell_type", assay = "RNA")

CellChatDB <- CellChatDB.human 

# set the used database in the object
melanoma@DB <- CellChatDB

```

# Preprocessing the expression data for cell-cell communication analysis


```{r vfnu}
# subset the expression data of signaling genes for saving computation cost
melanoma <- subsetData(melanoma) # This step is necessary even if using the whole database

melanoma <- identifyOverExpressedGenes(melanoma)

melanoma <- identifyOverExpressedInteractions(melanoma)

# project gene expression data onto PPI network (optional)
melanoma <- projectData(melanoma, PPI.human)

# Compute the communication probability and infer cellular communication network
melanoma <- computeCommunProb(melanoma)


# save df for predicted interactions
df.net.melanoma <- subsetCommunication(melanoma)


#write.csv(df.net.melanoma, file = "./cellchat_melanoma_interactions.csv", quote = F)


# Infer the cell-cell communication at a signaling pathway level
melanoma <- computeCommunProbPathway(melanoma)


# Calculate the aggregated cell-cell communication network
melanoma <- aggregateNet(melanoma)


```


```{r frnbgui}
# melanoma circle plot
groupSize <- as.numeric(table(melanoma@idents))

netVisual_circle(melanoma@net$count, vertex.weight = groupSize, weight.scale = T, label.edge= T, title.name = "Number of interactions", edge.label.cex = 0.5)
```

```{r}
netVisual_circle(melanoma@net$weight, vertex.weight = groupSize, weight.scale = T, label.edge= T, title.name = "Interaction weights/strength", edge.label.cex = 0.5)
```



# Compute the contribution of each ligand-receptor pair to the overall signaling pathway and visualize cell-cell communication mediated by a single ligand-receptor pair

```{r grnugi}
# show all the significant interactions (L-R pairs) associated with certain signaling pathways
netVisual_bubble(melanoma, sources.use = NULL, targets.use = NULL, signaling = c("TGFb"), remove.isolate = FALSE, font.size = 20)
```

```{r}
netVisual_chord_gene(melanoma, sources.use = NULL, targets.use = NULL, signaling = c("TGFb", "BMP", "GDF", "ACTIVIN"), lab.cex = 1)

```

```{r}
netVisual_chord_cell(melanoma, sources.use = NULL, targets.use = NULL, signaling = c("TGFb", "BMP", "GDF", "ACTIVIN"))

```



# Identify signaling groups based on their functional similarity

```{r vnbi}
melanoma <- computeNetSimilarity(melanoma, type = "functional")
melanoma <- netEmbedding(melanoma, type = "functional")
#> Manifold learning of the signaling networks for a single dataset
melanoma <- netClustering(melanoma, type = "functional") 

#> Classification learning of the signaling networks for a single dataset
# Visualization in 2D-space
netVisual_embedding(melanoma, type = "functional", label.size = 3.5)


```



# Saving cellchat object for shiny app

```{r rnugi}

saveRDS(melanoma, "cellchat.rds")


```

